Allocation scores, WIS, and CRPS via decision theory

### 2023-08-20 alloscore_manuscript/methods_apg.tex
add z to ias/crps

But 
\begin{align}
k = k(c,F) &= \sum_{l=1}^{N} F_l^{-1}(1-c/L) \\
\del{k}{c}& = \sum_{l=1}^{N} \frac{-1}{L f_l(q_{F_l,\tau(c)})} := -\mathrm{MAI}(c,F)\label{eqn:dkdc}
\end{align}
(where we assume that the $F_l$ have non-negative support). The name MAI refers to this derivative being the marginal total allocation increase for the total quantile loss Bayes act $x^{F,Q(C)}$ that results from a reduction of the cost $C$ of the resource by 1. Or in terms of the probability level $\tau(c)=1-c/L$,
\begin{align}
\del{k}{\tau} = \del{k}{c}\dby{c}{\tau} = -\mathrm{MAI}(c,F) \cdot (-L\tau) = L\mathrm{MAI}(c,F) \label{eqn:dkdtau}
\end{align}

>>>>

$s_{tQ}(x^{F,C,K}) \mid C = c, K = k$ in $\mathrm{AP}(k)$ coordinates:
\begin{align}
s_{tQ}(x^{F,c,k})(y) &= 
\begin{cases}
\sum_{l=1}^{N}L(y_l - x_l^{F,k})_{+} + ck, & k < \sum F_l^{-1}(1-c/L) \\
\sum_{l=1}^{N}L(y_l - x_l^{F,Q,c})_{+} + c(k - z_k(c)), & \text{otherwise, with } 
\end{cases} \\
z_k(c) &= (k -  \sum F_l^{-1}(1-c/L))_{+}
\end{align}

Let $k_1 = \sum F_l^{-1}(1-c_1/L)$ so that $x^{F,Q,c_1} = x^{F, k_1}$ and $z_{k_1}(\{c \leq c_1\}) = 0$, and take $0<c_a < c_1 < c_b < L$ and $0 < k_a < k_1 < k_b < K_2$.

Then with $K = k_1$ fixed, the path of functions $s_{k_1}(c) = s_{tQ}(x^{F,c,k_1})$ parametrized by $c \in [0,L]$ takes values
\begin{align}
s_{k_1}(0)  &= L\sum ( y_l-x_l^{F,k_1})_{+}  \\
s_{k_1}(c_a)  &= L\sum ( y_l-x_l^{F,k_1})_{+} + c_a k_1\\
s_{k_1}(c_1) &= L\sum (y_l - x_l^{F,k_1})_{+} + c_1 k_1  \\
s_{k_1}(c_b) &= L\sum (y_l - x_l^{F,Q, c_b})_{+} + c_b(k_1 - z_{k_1}(c_b)) \\
&= L\sum (y_l - x_l^{F,Q, c_b})_{+} + c_b \sum F_l^{-1}(1-c_b/L)\\
s_{k_1}(L)  &= L\sum {y_l}_{+}.
\end{align}

If instead $C = c_1$ is fixed, then $s_{c_1}(k) = s_{tQ}(x^{F,c_1,k})$ parameterized by 
$k \in [0,K_2]$ take values
\begin{align}
s_{c_1}(0) & = L \sum {y_l}_{+} \\
s_{c_1}(k_a) & = L \sum (y_l - x_l^{F,k_a})_{+} + c_1 k_a\\
& = L \sum (y_l - x_l^{F,Q,c(k_a)})_{+} + c_1 \sum F_l^{-1}(1-c(k_a)/L)\\
s_{c_1}(k_1) & = L \sum (y_l - x_l^{F,k_1})_{+} + c_1 k_1 \\
s_{c_1}(k_b) & = L \sum (y_l - x_l^{F,k_1})_{+} + c_1 (k_b - z_{k_b}(c_1)) \\
 & = L \sum (y_l - x_l^{F,k_1})_{+} + c_1 \sum F_l^{-1}(1-c(k_1)/L)\\
s_{c_1}(K_2) & = L \sum (y_l - x_l^{F,k_1})_{+} + c_1 (K_2 - z_{K_2}(c_1))
\end{align}

Writing $k(c) = \sum F_l^{-1}(1-c/L)$,
\begin{align}
s_{k_1}(c) - s_{c_1}(k(c)) &= (c-c_1)\sum F_l^{-1}(1-\max(c,c_1)/L) \\
s_{c_1}(k) - s_{k_1}(c(k)) &=  
\end{align}

But 
\begin{align}
\del{k}{c}& = \sum_{l=1}^{N} \frac{-1}{L f_l(q_{F_l,\tau(c)})} := -\mathrm{MAI}(c,F)\label{eqn:dkdc}
\end{align}
(where we assume that the $F_l$ have non-negative support). The name MAI refers to this derivative being the marginal total allocation increase for the total quantile loss Bayes act $x^{F,Q(C)}$ that results from a reduction of the cost $C$ of the resource by 1. Or in terms of the probability level $\tau(c)=1-c/L$,
\begin{align}
\del{k}{\tau} = \del{k}{c}\dby{c}{\tau} = -\mathrm{MAI}(c,F) \cdot (-L\tau) = L\mathrm{MAI}(c,F) \label{eqn:dkdtau}
\end{align}
